Young children rationally integrate semantic and pragmatic information sources to infer the meaning of words

### 2020-08-08 paper/manuscript.Rmd
ideas for expanded paper

>>>>

intorduce previous work (including modelling work) looking at inforamtion integration: Mostly lingusitc with pragmatic infotmation - however, no manipulation of lingusitc ususally.

More generally talk about quantitative models of child developmetn (review paper   gopnik and bonawitz, Sophie) and their usefulness in theory building.
